### 2019-03-14 metrics2_2.tex
metrics

\begin{enumerate}[(i)]
	\item \begin{align*}
	y_t - y_{t-1} = \lambda(\gamma_0 + \gamma_1 x_t + e_t - y_{t-1}) + a_t\\
	y_t = \lambda \gamma_0 + (1 - \lambda)y_{t-1} + \lambda \gamma_1 x_t + \lambda e_t + a_t\\
	\beta_0 = \lambda \gamma_0,\ \beta_1 = 1 - \lambda,\ \beta_2 = \lambda \gamma_1,\ u_t = \lambda e_t + a_t
	\end{align*}
	\item Since
	\begin{align*}
	\expect[u_t|x_t, y_{t-1}, x_{t-1}, \dots] = 0
	\end{align*}
	and series are weakly dependent then we can consistently estimate $\beta_j$ by OLS regressing $y_t$ on $y_{t-1}, x_{t}$.
	\item \begin{align*}
	\hat{\lambda} = 1 - \hat{\beta}_1 = 0.3\\
	\hat{\gamma}_1 = \frac{\hat{\beta}_2}{\hat{\lambda}} \approx 0.67
	\end{align*}
\end{enumerate}
\end{document}

>>>>

\begin{enumerate}[(i)]
	\item \begin{align*}
	y_t - y_{t-1} = \lambda(\gamma_0 + \gamma_1 x_t + e_t - y_{t-1}) + a_t\\
	y_t = \lambda \gamma_0 + (1 - \lambda)y_{t-1} + \lambda \gamma_1 x_t + \lambda e_t + a_t\\
	\beta_0 = \lambda \gamma_0,\ \beta_1 = 1 - \lambda,\ \beta_2 = \lambda \gamma_1,\ u_t = \lambda e_t + a_t
	\end{align*}
	\item Since
	\begin{align*}
	\expect[u_t|x_t, y_{t-1}, x_{t-1}, \dots] = 0
	\end{align*}
	and series are weakly dependent then we can consistently estimate $\beta_j$ by OLS regressing $y_t$ on $y_{t-1}, x_{t}$.
	\item \begin{align*}
	\hat{\lambda} = 1 - \hat{\beta}_1 = 0.3\\
	\hat{\gamma}_1 = \frac{\hat{\beta}_2}{\hat{\lambda}} \approx 0.67
	\end{align*}
\end{enumerate}

\section*{Problem 3}
Suppose that the equation 
\begin{align*}
y_t = \alpha + \delta _t + \beta_1 x_{t1}+\dots+\beta_k x_{tk}+u_t
\end{align*} satisfies the sequential exogeneity assumption in equation (11.40). 
\begin{enumerate}[(i)]
\item Suppose you difference the equation to obtain 
\begin{align}\label{eq1}
\Delta y_t = \delta +\beta_1 \Delta x_{t1} + \dots+ \beta_k \Delta x_{tk} + \Delta u_t.
\end{align}
How come applying OLS on the differenced equation does not generally result in consistent estimators of the $\beta_j$?
\item What assumption on the explanatory variables in the original equation would ensure that OLS on the differences consistently estimates the $\beta_j$?
\item Let $z_{t1},\dots, z_{tk}$ be a set of explanatory variables dated contemporaneously with $y_t$. If we specify the static regression model $y_t = \beta_0 + \beta_1z_{t1} +\dots+ \beta_k z_{tk} + u_t$, describe what we need to assume for $x_t = z_t$ to be sequentially exogenous. Do you think the assumptions are likely to hold in economic applications?
\end{enumerate}

\begin{enumerate}
	\item First of all, since we do not have any assumptions about the model apart from sequential exogeneity
	\begin{align*}
	\expect[u_t|\vec{x}_t, \vec{x}_{t-1}, \dots] = \expect[u_t] = 0
	\end{align*}
	we can have a perfect multicollinearity among $\vec{x}_t$. Assume for example $k = 3$, and the model is:
	\begin{align*}
	y_t =\alpha + \delta t + \beta_1 x_t + \beta_2 z_t + \beta_3 w_t + u_t
	\end{align*} 
	where $w_t = x_t + z_t\ \forall\ t$. In this case obviously $\Delta w_t = \Delta x_t + \Delta z_t$ and the OLS estimate for \eqref{eq1} is inconsistent.
	\item To ensure that OLS for \eqref{eq1} is consistent. Assumptions TS1'-TS3' should hold. The process \eqref{eq1} should be weakly dependent (and stationary)
\end{enumerate}
\end{document}
